### 2021-02-14 Chapter-1/Chapter-1.tex
update

\section{Limitations of Existing Side Channel Vulnerability Detection Works}
Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage site for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.

@@

\section{Trace-oriented Binary Analysis}
Binary analysis is the process of automatically inferring program behaviors from
the binary executable.
It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
available. Besides, some low-level information, including memory accesses and cache
accesses, is only available on the binary code level. As many side-channel vulnerabilities
are typically low-level problem, we believe binary analysis are more suitable than
source code level analysis.

>>>>

\section{Side-channel}

\subsection{Attacks}

\subsection{Defense}

Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage site for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.

@@

\section{Binary Analysis}
Binary analysis is the process of automatically inferring program behaviors from
the binary executable.
It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
available. Besides, some low-level information, including memory accesses and cache
accesses, is only available on the binary code level. As many side-channel vulnerabilities
are typically low-level problem, we believe binary analysis are more suitable than
source code level analysis.
